Constraint Validation with OWL 2 | Closed World Semantics | With and Without Reasoning

### 2014-10-04 paper/paper2.tex
separate constraint and axioms

>>>>

\section{separate constraints and axioms}

\subsection{disjointness}

A disjointness constraint is actually different (both
semantically and in practice) from the OWL disjointness axiom. I see no
problem with adding disjointness to an AP where such disjointness is
needed in the applications that will use the AP (data creation, quality
control, documentation of your "data set"). In fact, I believe I have
seen such constraints being used in validation functions that use
SPARQL, and it doesn't seem to be a problem. As we know (and Tom and I
will show some examples in Austin), disjointness in the open world can
be ill-advised precisely because it does not mean the same as
disjointness in the closed world. In the closed world it may be a common
requirement; in the open world it can greatly interfere with data
compatibility. The same is true of cardinality (which has a very
different meaning in the open world).

I do not see APs as duplicating the OWL axioms -- although the natural
language terms we use may be the same, the functionality is quite different.

Obviously, this is what we need to keep in mind as we go through our use
cases. I don't know what problems might arise when we get into the details.
